Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-03-26 document/ms.tex
bugfix
formatting shit

\newcommand{\nyu}{2}
\newcommand{\mpia}{3}
\newcommand{\princeton}{4}
\author{%
    Daniel~Foreman-Mackey\altaffilmark{1,\nyu},
    David~W.~Hogg\altaffilmark{\nyu,\mpia},
    Timothy~D.~Morton\altaffilmark{\princeton},
    Erik~Petigura\altaffilmark{\berkeley},
    \etal
}
\altaffiltext{1}         {To whom correspondence should be addressed:
                          \url{danfm@nyu.edu}}
\altaffiltext{\nyu}      {Center for Cosmology and Particle Physics,
                          Department of Physics, New York University,
                          4 Washington Place, New York, NY, 10003, USA}
\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\princeton}{Department of Astrophysics, Princeton University,
                          Princeton, NJ, 08540, USA} % CHECK THIS ZIP CODE
\altaffiltext{\berkeley} {Department of Astronomy, University of California at Berkeley,
                          Berkeley, CA, XXXXX, USA} % CHECK THIS ZIP CODE

\begin{abstract}
Although no true extra-solar Earth analog is known,
  hundreds of planets have been found around Sun-like stars
  that are either Earth-sized but on shorter periods,
  or else on year-long orbits but somewhat bigger than Earth.
These populations ought to permit a
  (possibly highly uncertain)
  extrapolated measurement of the probability or rate at which Sun-like stars host true Earth analogs.
Here we build a set of probabilistic models of the population of known small planets around G dwarfs.
The models all take into account the transit probability and the completeness (or detection efficiency)
  as a function of planet radius and orbital period.
Because we forward model the data,
  we do not ever have to perform the traditional weighting of the data by the inverse detection efficiency;
  our inferences are more precise than those produced by traditional methods.
Our most sophisticated models do not assume that the joint radius--period distribution is separable,
  and correctly take into account the significant observational uncertainties on the planet radii,
  using the machinery of hierarchical inference.
We reconsider and confirm with weaker assumptions
  prior results on the distribution of exoplanet radii
  that show a flattening of the distribution below a few Earth radii.
One output of our models is fully marginalized estimates---%
  marginalizing out observational uncertainties and all distribution parameters---%
  of the rate density of true Earth analogs,
  expressed as a number of planets per star per natural logarithmic interval of radius and period,
  evaluated at the properties of Earth.
The rate density we infer depends strongly on the permitted flexibility of the distribution model,
  but tends to come out around ten percent, with large uncertainty.
\end{abstract}

>>>>

\newcommand{\nyu}{2}
\newcommand{\mpia}{3}
\newcommand{\princeton}{4}
\newcommand{\berkeley}{5}
\author{%
    Daniel~Foreman-Mackey\altaffilmark{1,\nyu},
    David~W.~Hogg\altaffilmark{\nyu,\mpia},
    Timothy~D.~Morton\altaffilmark{\princeton},
    Erik~A.~Petigura\altaffilmark{\berkeley},
    \etal
}
\altaffiltext{1}         {To whom correspondence should be addressed:
                          \url{danfm@nyu.edu}}
\altaffiltext{\nyu}      {Center for Cosmology and Particle Physics,
                          Department of Physics, New York University,
                          4 Washington Place, New York, NY, 10003, USA}
\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\princeton}{Department of Astrophysics, Princeton University,
                          Princeton, NJ, 08540, USA} % CHECK THIS ZIP CODE
\altaffiltext{\berkeley} {Department of Astronomy,
                          University of California at Berkeley,
                          Berkeley, CA, XXXXX, USA} % CHECK THIS ZIP CODE

\begin{abstract}
Although no true extra-solar Earth analog is known, hundreds of planets have
been found around Sun-like stars that are either Earth-sized but on shorter
periods, or else on year-long orbits but somewhat bigger than Earth.
These populations ought to permit a (possibly highly uncertain) extrapolated
measurement of the probability or rate at which Sun-like stars host true Earth
analogs.
Here we build a set of probabilistic models of the population of known small
planets around G dwarfs.
The models all take into account the transit probability and the completeness
(or detection efficiency) as a function of planet radius and orbital period.
Because we forward model the data, we do not ever have to perform the
traditional weighting of the data by the inverse detection efficiency.
Our most sophisticated models do not assume that the joint radius--period
distribution is separable, and correctly take into account the significant
observational uncertainties on the planet radii, using the machinery of
hierarchical inference.
We reconsider and confirm with weaker assumptions prior results on the
distribution of exoplanet radii that show a flattening of the distribution
below a few Earth radii.
One output of our models is fully marginalized estimates---marginalizing out
observational uncertainties and all distribution parameters---of the rate
density of true Earth analogs, expressed as a number of planets per star per
natural logarithmic interval of radius and period, evaluated at the properties
of Earth.
The rate density we infer depends strongly on the permitted flexibility of the
distribution model, but tends to come out around ten percent, with large
uncertainty.
\end{abstract}
